\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[scaled=0.92]{helvet}
\usepackage{fontawesome} % Add this for the URL icon
\renewcommand{\familydefault}{\sfdefault}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
% Modified spacing for technical skills section
\newcommand{\skillItem}[1]{\item\small{#1 \vspace{-1pt}}}
% Modified resumeSubheading command with reduced spacing
\newcommand{\resumeSubheading}[4]{\vspace{-3pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\ \textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-9pt}}

% Modified project heading to include URL logo and make title a link
\newcommand{\resumeProjectHeading}[3]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small{\faLink} \small{\href{#3}{\underline{\textbf{#1}}}} \small{| \emph{#2}} \\
\end{tabular*}\vspace{-7pt}}

% Modified to add custom spacing between items
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.25in, itemsep=1pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
% New command for tighter spacing in skills section
\newcommand{\skillListStart}{\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-3pt]}
\newcommand{\skillListEnd}{\end{itemize}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Aayush Panda} \\ \vspace{1pt}
    \small \href{mailto:aayush.vinayak@gmail.com}{aayush.vinayak@gmail.com} $|$
    \href{https://linkedin.com/in/aayush-panda}{linkedin.com/in/aayush-panda} $|$
    \href{https://github.com/AayushPanda}{github.com/AayushPanda}
\end{center}

\section{Technical Skills}
\skillListStart
    \skillItem{\textbf{Programming Languages:} C, C++, Rust, Python, Java, TypeScript, SQL, Haskell, Scheme, Bash, HTML/CSS, x86 assembly}
%     \skillItem{\textbf{Web \& Mobile Development:} Next.js, React, Flutter, Android Development, Node.js, Express, Firebase}
%     \skillItem{\textbf{Cloud \& DevOps:} Google Cloud Platform (GCP), Docker, Git, GitHub Actions, Linux/Unix Environments}
    \skillItem{\textbf{Data Science \& Machine Learning:} NumPy, Pandas, sklearn, PyTorch, TensorFlow, Keras, OpenCV, Matplotlib, Seaborn, Jupyter}
    \skillItem{\textbf{Databases:} SQL dbs, Firestore, Neo4J, Chroma}
\skillListEnd

\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading{University of Waterloo}{\textbf{GPA: } 3.92/4.00}{Bachelor of Computer Science, Honours Co-op}{Sep. 2024 -- Apr. 2029}
%     \resumeItem{Relevant Coursework: Functional Programming, Algo Design and Data Abstraction, Data Structures and Data Management (All advanced)}
\resumeSubHeadingListEnd
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading{ML \& NLP Engineer}{Sep. 2025 -- Present}{Huawei Canada}{}
    \resumeItemListStart
        \resumeItem{Working on knowledge graph generation, named entity resolution, semantic algorithms for edit targeting for Xiaoyi Canvas (similar to ChatGPT canvas)}
    \resumeItemListEnd

    \resumeSubheading{Laboratory Assistant}{Apr. 2025 -- Present}{University of Waterloo Multi-Sensory Brain and Cognition Lab (MBC)}{}
    \resumeItemListStart
        \resumeItem{Developed CV pipelines and algorithms for baseball/eye tracking for an ongoing research project on how batsmen's eyes track baseballs through various jumps and saccades}
        \resumeItem{Developed correspondence algorithm to synchronise data from high speed head mounted camera and eye tracking data}
        \resumeItem{Working on information-theoretic modeling of human visual perception}
    \resumeItemListEnd

    \resumeSubheading{Undergraduate Research Assistant}{Apr. 2025 -- Aug. 2025}{University of Waterloo}{}
    \resumeItemListStart
        \resumeItem{Research on private record linkage protocols using locality sensitive hashing, supervised by Dr. Florian Kerschbaum}
        \resumeItem{Developed a differentially private method of estimating max LSH bin, to allow for private frequency smoothing without sharing bin size info between parties (which leaks information)}
        \resumeItem{Developed k-d cuckoo hashing algorithm for private set intersection using the backing array}
    \resumeItemListEnd

    \resumeSubheading{Software Engineering Intern}{Mar. 2025 -- Apr. 2025}{Toma (YC W25)}{}
    \resumeItemListStart
        \resumeItem{Wrote a service that evalutes dealership customer support quality using a conversational voice AI built with ElevenLabs. This data was then used to find ideal clients, and demonstrate/evaluate Toma's impact on dealerships.}
        \resumeItem{Developed a server log viewer with IDE-like features to improve debugging efficiency.}
        \resumeItem{Worked on model evaluation for Toma's voice agents}
    \resumeItemListEnd

\resumeSubHeadingListEnd


\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading{Concord}{Rust, Vulkan, HLSL}{}
    \resumeItemListStart
        \resumeItem{Ongoing project to build a cross-platform runtime in Rust for hardware accelerated computation, with a unified ISA and memory model for CPU/GPU operations.}
    \resumeItemListEnd

    \resumeProjectHeading{Semantify}{Python, React, FastAPI, Sentence Transformers, UMAP, Ollama}{https://github.com/AayushPanda/semantify}
    \resumeItemListStart
        \resumeItem{Built a system that semantically organises \textbf{1000+ files} into a directory structure in minutes using embedding models and custom hierarchical clustering and subtree merging algorithms}
        \resumeItem{Developed an interactive visualization of document embeddings to allow intuitive semantic exploration}
        \resumeItem{Implemented a RAG-powered chat interface to intelligently query uploaded documents with source citation}
    \resumeItemListEnd

    \resumeProjectHeading{Phased Array SONAR}{C++, Python, Xtensa LX6 microprocessor, AVR RISC processors}{https://github.com/AayushPanda/phased-array-sonar}
    \resumeItemListStart
        \resumeItem{Engineered a sub-degree precision beam-steering phased SONAR array with real-time radar-style display on oscilloscopes.}
        \resumeItem{Designed a waveguide to reduce inter-element pitch and suppress grating lobes, enhancing beam directivity.}
        \resumeItem{Built a phased array simulator suite to visualize beamforming, steering, and focus behaviors in 2D.}
    \resumeItemListEnd

%     \resumeProjectHeading{Woodlands App}{Flutter, Firebase, Google Cloud Storage}{https://github.com/Woodlands-App-Team/WAPP}
%     \resumeItemListStart
%         \resumeItem{Developed a \textbf{Flutter} app to inform students about announcements, events, and cafeteria menu.}
%         \resumeItem{Integrated \textbf{Firebase} and \textbf{Google Cloud Storage} for authentication and data storage.}
%         \resumeItem{Achieved \textbf{400+} regular monthly users and rank \textbf{40} on the Apple App Store's top charts.}
%     \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Patents}
\skillListStart
    \resumeItem{\textbf{CA 3222437:} Device for redirection of optical beams using virtual gratings generated by stationary waves.}
    \resumeItem{\textbf{CA 3119717:} Compliant mechanism for operating flight control surfaces of a remotely piloted aircraft.}

\skillListEnd

\section{Awards}
\skillListStart
    \resumeItem{\textbf{University of Waterloo President's Research Award}}
    \resumeItem{\textbf{Jane Street Estimathon @ UWaterloo (2024):} First place}
    \resumeItem{\textbf{Hack the North 2022:} Winner (out of 829 participants)}
    \resumeItem{\textbf{PicoCTF 2022:} 2nd place in Canada, 14th (top 0.001\%) globally}
    \resumeItem{\textbf{FIRST Innovation Challenge 2021:} Semifinalist}
\skillListEnd


\end{document}
